Testing atlantisom: true biomass output from Atlantis

### 2019-05-21 Atlantisom2SSworkflowtest.Rmd
start comparison with catch bio

>>>>

#just try the three species for now
catchbio_census_ss <- create_fishery_subset(dat = truth$catchbio,
                                         time = timeall,
                                         species = spp.name,
                                         boxes = boxall)

#does it match catch.txt (which should be in tons)?
atCtxt <- read.table(file.path(d.name, catch.file), header=T)

atCtxttidy <- atCtxt %>%
  select(Time:XXX) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, catchbio, -Time) %>%
  filter(species %in% levels(catchbio_census_ss$species))
